Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 bckground.tex
comments on related work.

>>>>

\jhanote{In this section we should talk less about PanDA and more about other
WMS -- highlighting the fact that (i) there isn't a comprehensive systems
(design, architecture and execution properties) discussion of other WMS so
difficult to compare, (ii) real comparison should be to the Gliden-in WMS
ecosystem and use this as opportunity to narrate the reasons for the
divergence. Also might this section be moved towards the rear, as this is 
a practice paper and not a traditional research paper?}
